Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-14 paper.tex
Added a couple of points to come back to

  By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
  $g_i^{-1}(H_{i-1})$, so the definition of $p^\infty_{n_i}$ implies that a 
  geodesic ray $\alpha_i$ from $e$ to $g_i^{-1}(\zeta_i)$ does not pass through 
  $g_i^{-1}(H_{i-1})$. Equivalently, $g_i\composed\alpha_i$ is a geodesic from 
  $g_i$ to $\zeta_i$ that does not pass through $H_{i-1}$.

@@

  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 
  in $H$ of $C$.  After passing to a subsequence these geodesic rays converge to 
  a bi-infinite geodesic passing through the star in $H$ of $C$, both end points 
  of which must be $\xi$, which is a contradiction.
\end{proof}

>>>>

  \todo{This assumption is gone.}
  By assumption, $g_i^{-1}(H_i)$ contains the star in $K_{n_i}$ of 
  $g_i^{-1}(H_{i-1})$, so the definition of $p^\infty_{n_i}$ implies that a 
  geodesic ray $\alpha_i$ from $e$ to $g_i^{-1}(\zeta_i)$ does not pass through 
  $g_i^{-1}(H_{i-1})$. Equivalently, $g_i\composed\alpha_i$ is a geodesic from 
  $g_i$ to $\zeta_i$ that does not pass through $H_{i-1}$.

@@

  \todo{Is star actually the right word?}
  Then for each $i$ a geodesic from $g_i$ to $\zeta_i$ passes through the star 
  in $H$ of $C$.  After passing to a subsequence these geodesic rays converge to 
  a bi-infinite geodesic passing through the star in $H$ of $C$, both end points 
  of which must be $\xi$, which is a contradiction.
\end{proof}
